---
title: "Infektionsdetektiven"
author: "Bastian Ilsø Hougaard, Hendrik Knoche"
date: "6/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RMySQL)
library(tidyr)
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)
library(data.table)
options(digits.secs = 4) # enable millisecond display in console.
creds <- read.csv("credentials.csv", header=TRUE,sep=",", colClasses=c("character","character","character","character"))
lapply( dbListConnections( dbDriver( drv = "MySQL")), dbDisconnect)
mydb = dbConnect(MySQL(),
                 user=creds[1, "username"],
                 # rstudioapi::askForPassword("Database user"),
                 password=creds[1, "password"],
                 # rstudioapi::askForPassword("Database password"),
                 dbname=creds[1, "dbname"],
                 host=creds[1, "host"])

RetreiveDataSet <- function(tablename, column, colvalue) {
  queryString = "SELECT *"
  queryString = paste(queryString, "FROM",tablename, sep = " ")
  if (colvalue != "NA") {
    queryString = paste(queryString, "WHERE",column,"= ",sep=" ")
    queryString = paste(queryString,"\'",colvalue,"\'",sep="")
  }
  print(queryString)
  res = dbSendQuery(mydb, queryString)
  df = fetch(res, n=-1)
  dbClearResult(dbListResults(mydb)[[1]])
  return(df)
}

df <- RetreiveDataSet("infektionsdetektiven_event","NA","NA")
```

## Introduction

We investigate whether how much time was spent looking at graphs and indicators of stress during the game.

## Overview Stats


```{r overview, echo=FALSE}
overview <- df %>%
  summarize(
    no_of_plays = length(unique(SessionID)),
    played_from = min(Timestamp),
    played_to = max(Timestamp)
  )
kable(overview) # formats the output as a nice table.
```

## Filtered by Experiment
Lets examine the data specifically from the day where the classrooms were trying out the game.


```{r experiment-stats, echo=FALSE}
df$Timestamp <- as.POSIXct(df$Timestamp, format = "%Y-%m-%d %H:%M:%OS")
experiment_start = as.POSIXct("2020-06-11 07:00:00.000", format = "%Y-%m-%d %H:%M:%OS")
experiment_end = as.POSIXct("2020-06-11 16:00:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_3_start = as.POSIXct("2020-06-11 07:45:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_3_ended = as.POSIXct("2020-06-11 09:15:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_4_start = as.POSIXct("2020-06-11 09:45:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_4_ended = as.POSIXct("2020-06-11 11:55:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_5_start = as.POSIXct("2020-06-11 12:40:00.000", format = "%Y-%m-%d %H:%M:%OS")
grade_5_ended = as.POSIXct("2020-06-11 14:45:00.000", format = "%Y-%m-%d %H:%M:%OS")


df_experiment <- df %>%
  filter( Timestamp > experiment_start & Timestamp < experiment_end)
df_grade3  <- df %>%
  filter( Timestamp > grade_3_start & Timestamp < grade_3_ended)
df_grade4  <- df %>%
  filter( Timestamp > grade_4_start & Timestamp < grade_4_ended)
df_grade5  <- df %>%
  filter( Timestamp > grade_5_start & Timestamp < grade_5_ended)
```

### Third Grade Data

``` {r third-grade, echo=FALSE}
summaries <- df_grade3 %>%
  group_by(SessionID) %>%
  summarize(
    played_time = difftime(max(Timestamp), min(Timestamp), units = "min"),
    levels_played = sum(Event == "GameInit"),
    count = length(Timestamp),
    level_reached = max(LevelNo),
    device_id = max(DeviceID),
  )
kable(summaries)
```

### Fourth Grade Data

``` {r fourth-grade, echo=FALSE}
summaries <- df_grade4 %>%
  group_by(SessionID) %>%
  summarize(
    played_time = difftime(max(Timestamp), min(Timestamp), units = "min"),
    levels_played = sum(Event == "GameInit"),
    count = length(Timestamp),
    level_reached = max(LevelNo),
    device_id = max(DeviceID),
  )
kable(summaries)
```

### Fifth Grade Data

``` {r fifth-grade, echo=TRUE}
summaries <- df %>%
  group_by(SessionID) %>%
  summarize(
    played_time = difftime(max(Timestamp), min(Timestamp), units = "min"),
    levels_played = sum(Event == "GameInit"),
    count = length(Timestamp),
    level_reached = max(LevelNo),
    device_id = max(DeviceID),
  )
kable(summaries) 
```

### Mutating variables

``` {r fifth-grade-stats, echo=FALSE}
add_level_ID <- df_grade5 %>%
  group_by(PlayID)%>%
  mutate(
    flag = (Event == 'NextLevel'),
    levelBin = ifelse(flag,1,0),
    levelID = cumsum(levelBin),
    flag = NULL,
    levelBin = NULL
  ) %>% arrange(PlayID, Timestamp) %>% ungroup()

df_nextleveltimestamp <- 
  add_level_ID %>%
  select(PlayID, LevelNo, Event, Timestamp) %>%
  filter(Event == 'NextLevel') %>% 
  rename(
    next_level_stamp = Timestamp,
  ) %>% select(-Event)

df_merge <- add_level_ID %>% left_join(df_nextleveltimestamp)

df_viewstats_summary <- 
  df_merge %>%
  select(PlayID, LevelNo, Event, Timestamp, next_level_stamp) %>%
  filter(Event == "ViewingStatistics") %>%
    mutate(
      view_time = difftime(next_level_stamp, Timestamp, units= "sec"),
      ) %>% select(-Event)

df_grade5_merge <- df_merge %>% left_join(df_viewstats_summary)

df_grade5_merge%<>%
  group_by(PlayID)%>%
    mutate(
      max_level_reached = max(LevelNo),
      total_played_time = difftime(max(Timestamp), min(Timestamp), units = "sec"),
      player_id=group_indices(),
      ) %>% arrange(PlayID, Timestamp)
df_grade5_merge%>%filter(Event == 'NextLevel')
p1<-ggplot(df_grade5_merge[df_grade5_merge$view_time<250 & df_grade5_merge$total_played_time<500,], aes(x=as.numeric(view_time), y=as.numeric(total_played_time), color=as.factor(player_id)))
```


# Plots


```{r total-time-played-plot, echo=FALSE}
p1 + geom_jitter(size=1, width=.1, height=.1) + 
theme_bw() +
labs(title="Total time played against statistics view time") +
xlab("Stats view time") +
ylab("Total time played") + 
scale_y_log10()

```
## Plot text


```{r total-time-played-faceted-plot, echo=FALSE}
p1 + geom_jitter(size=1) + 
facet_grid(. ~ LevelNo) + 
theme_bw() +
labs(title="Facet of total time played against statistics view time",
     subtitle="Facets are level number", 
     caption="Stats view time values above 250 deemed to be idle, and filtered out") +
xlab("Stats view time") + 
ylab("Total time played") +
scale_y_log10()
```
## Plot text

```{r level-reached-plot, echo=FALSE}
p2 <- ggplot(df_grade5_merge[df_grade5_merge$view_time<250,], aes(x=as.numeric(view_time), y=max_level_reached, color=as.factor(player_id)))

p2 + geom_point(size=1, alpha=.3) + 
theme_bw() +
labs(title="Max level reached against statistics view time") + 
xlab("Stats view time") + 
ylab("Max level reached")
```
## Plot text
  
```{r, echo=FALSE}
df_grade5_stars<-
  df_grade5_merge %>% 
  group_by(PlayID)%>%
  select(PlayID, LevelNo, Event) %>%
    summarise(
      stars_amount_all = sum(Event =="GotInfectionStarAward", Event=="GotIsolationStarAward", Event=="GotVaccinationStarAward"),
      stars1 = sum(Event == "GotInfectionStarAward"),
      stars2 = sum(Event == "GotIsolationStarAward"),
      stars3 = sum(Event == "GotVaccinationStarAward"),
      stars4 = stars1 + stars2 + stars3,
      reload_amount = sum(Event == "ReloadingLevel")
      )

df_grade5_final <- df_grade5_merge %>% merge(df_grade5_stars)

med<-median(df_grade5_final$stars_amount_all)

#er der nogle playID's som har klaret sig bedre -> infection(1), isolation(2) og vaccination(3) stars
ggplot(df_grade5_final, aes(x=as.factor(player_id), y=stars_amount_all, color=as.factor(player_id))) + geom_point() + theme_bw()+ 
geom_hline(aes(yintercept=med))

df_grade5_viewstats<-
  df_grade5_final %>%
  filter(Event == "ViewingStatistics")

#selecting upper half grade5 only
df_grade5_upper<-
  df_grade5_final %>% 
  filter(Event == "ViewingStatistics" & stars_amount_all>med)

#selecting middle ground grade5 only
df_grade5_middle<-
  df_grade5_final%>%
  filter(Event == "ViewingStatistics" & stars_amount_all==med)

#selecting lower half grade5 only
df_grade5_lower<-
  df_grade5_final%>%
  filter(Event == "ViewingStatistics" & stars_amount_all<med)

#view_stats mod levelno - viser hvor meget der er blevet kigget på stats efter hvert levelno
ggplot(df_grade5_viewstats ,aes(x=LevelNo, y=as.numeric(view_time), color=as.factor(player_id))) + 
geom_jitter(size=1) +
theme_bw() + labs(title="all") + scale_x_continuous(name="Level", limits=c(0, 7)) + 
scale_y_continuous(name="Statistics Viewtime", limits=c(0,100))

ggplot(df_grade5_upper,aes(x=LevelNo, y=as.numeric(view_time), color=as.factor(player_id))) + 
geom_jitter(size=1) +
theme_bw() + labs(title="upper") + scale_x_continuous(name="Level", limits=c(0, 7)) + 
scale_y_continuous(name="Statistics Viewtime", limits=c(0,100))

ggplot(df_grade5_middle,aes(x=LevelNo, y=as.numeric(view_time), color=as.factor(player_id))) + 
geom_jitter(size=1) +
theme_bw() + labs(title="middle") + scale_x_continuous(name="Level", limits=c(0, 7)) + 
scale_y_continuous(name="Statistics Viewtime", limits=c(0,100))

ggplot(df_grade5_lower,aes(x=LevelNo, y=as.numeric(view_time), color=as.factor(player_id))) + 
geom_jitter(size=1) +
theme_bw() + labs(title="lower") + scale_x_continuous(name="Level", limits=c(0, 7)) + 
scale_y_continuous(name="Statistics Viewtime", limits=c(0,100))

#ReloadingLevel og levelno, kigger de mere på stats når de reloader spillet
ggplot(df_grade5_viewstats, aes(x=reload_amount, y=as.numeric(view_time), color=as.factor(player_id))) + 
geom_jitter(, size=1) + 
theme_bw() + facet_grid(. ~ LevelNo) + labs(title ="all") + scale_y_continuous(name="Statistics Viewtime", limits=c(0,100))
```

## Thoughts on upper, middle, lower bracket plots
In the upper/middle bracket, people seem to skip the stats page rather quickly, while the lower bracket are looking at the stats page a bit more. Could this be because the lower bracket would be looking for answers on the stats page on how to improve within the game?

